Verifying Demonstrations

### 2018-05-25 paper/properties.tex
Adds comment to properties

In our setting, we have three potential adversaries: Alice, Grace and Mallory.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
\daniel{Changed back to Grace since that's what's in the intro now.}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
count but also additionally to deanonymize some of the participants in order to 
arrest them or forcefully convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in 
affecting the stability of Grace's regime, for Mallory's own gain, thus 
supporting either Grace or Alice as she see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Grace}
In addition, Mallory could also have simply as her objective to cause a 
denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will formally define some security 
properties specifying the computational effort needed by the adversaries to 
succeed.

>>>>

In our setting, we have three potential adversaries: Alice, Grace and Mallory.
\seb{I changed the name of Grace to Eve to be consistent with the introduction}
\daniel{Changed back to Grace since that's what's in the intro now.}
Alice is a participant to the protest and thus she might be also interested in manipulating the system to increase the count (\eg she might have an incentive to do so as an activist).
In contrast, the aim of Grace, the totalitarian dictator, is to decrease the 
count but also additionally to deanonymize some of the participants in order to 
arrest them or forcefully convince them to change their minds.
Finally, Mallory represents another nation state and has some interest in 
affecting the stability of Grace's regime, for Mallory's own gain, thus 
supporting either Grace or Alice as she see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Grace}
\daniel{I think that we can move Mallory to the discussion, because Mallory 
  cannot get valid credentials for herself as a foreign state.}
In addition, Mallory could also have simply as her objective to cause a 
denial-of-service attack on the architecture of \PRIVO.
In the following two subsections, we will formally define some security 
properties specifying the computational effort needed by the adversaries to 
succeed.
